---
title: "Main Script"
author: "Group 7"
date: "November 1, 2016"
output: html_document
---

This is adpated from the template of Yuting Ma for running experiments of image analysis (or any predictive modeling). The R script can be found in main.R. 

### Specify directories
Set the working directory to the image folder. Specify the training and the testing set. For data without an independent test/validation set, you need to create your own testing data by random subsampling. In order to obain reproducible results, set.seed() whenever randomization is used. 
```{r, eval=FALSE}
setwd("~/Google Drive/Columbia/5243 ADS/Project 3/Fall2016-proj3-grp7")
```

```{r}
img_train_dir <- "~/Google Drive/Columbia/5243 ADS/Project 3/Project3_poodleKFC_train/images"
img_test_dir <- "./data" #change this directory when testing
```

### Import training images class labels
For labradoodle dogs vs fried chicken, we code chicken as "1" and dogs as "0" for binary classification.
```{r}
# label_train <- c(rep("1",1000),rep("0",1000))
```

### Construct visual features
For our project, we construct 512 RGB features. Save the constructed features to the output subfolder.
```{r}
source("./lib/feature.R")
load("./output/5512Feature_eval.RData")
dat_train <- Feature_eval
tm_feature_train <- system.time(dat_train <- feature(img_train_dir, "img_zip_train"))

dat_test=feature(img_test_dir, "/TestImages/Img")
tm_feature_test <- system.time(dat_test <- feature(img_test_dir, "/TestImages/Img")) #12:14
save(dat_train, file="./output/feature_train.RData")
save(dat_test, file="./output/feature_test.RData")
```

### Train a classification model with training images
Call the train model and test model from library. 
```{r}
source("./lib/Final Train.R")
source("./lib/test.R")
```


* Train the model with the entire training set using the selected model (model parameter) via cross-validation.
```{r}
tm_train <- system.time(fit_train <- train(dat_train, label_train)) #10:36
save(fit_train, file="./output/fit_train.RData")
```

### Make prediction 
Feed the final training model with the completely holdout testing data. 
```{r}
tm_train
tm_test <- system.time(pred_test <- test(fit_train, dat_test))
save(pred_test, file="./output/pred_test.RData")
```

### Summarize Running Time
Prediction performance matters, do does the running times for constructing features and for training the model, especially when the computation resource is limited. 
```{r}
cat("Time for constructing training features=", tm_feature_train[1], "s \n")
cat("Time for constructing testing features=", tm_feature_test[1], "s \n")
cat("Time for training model=", tm_train[1], "s \n")
cat("Time for making prediction=", tm_test[1], "s \n")
```
