---
title: "Image Feature Exploration"
output: html_notebook
---

I manually picked 12 representatives from each category:

chicken_0116
chicken_0131 (so hard to distinguish)
chicken_0181
chicken_0218
chicken_0264
chicken_0306
chicken_0383
chicken_0761
chicken_0646
chicken_0599 (only a leg)
chicken_0891 (dark color)
chicken_0999

dog_0010
dog_0021 (typical hair)
dog_0023
dog_0033
dog_0095
dog_0146 (only a leg)
dog_0147
dog_0342 (smooth surface)
dog_0404
dog_0432
dog_0608
dog_0887


Some ideas:
- Extract surface texture which stands out with curvy grains (? hard to realize)
- Color RGB feature (success, 800 of them)
- Color HSV feature


Here I pick 5 images (3 fried chickens and 2 dogs) to do an image exloration demo.
```{r}
setwd("~/Google Drive/Columbia/5243 ADS/Project 3/Project3_poodleKFC_train/images")

library("EBImage")
i1.c <- readImage("chicken_0116.jpg") #chicken 1
i2.c <- readImage("chicken_0761.jpg") #chicken 2
i1.d <- readImage("dog_0021.jpg") #dog 1
i2.d <- readImage("dog_0608.jpg") #dog 2
i1 <- readImage("chicken_0131.jpg") # hard-to-distinguish chicken

filename=list(i1.c,i2.c,i1.d,i2.d,i1) #list all 5 images

options("EBImage.display"= "raster") #display in R rather than in browser

print(filename) #detailed info of all 5 images 

for (i in 1:5){
  display(filename[[i]])   #display images
  hist(filename[[i]])      #RGB histograms
}
```


#Change to Greyscale, blue and red channels
```{r}
file.bw=list()
file.bl=list()
file.red=list()

for (i in 1:5){
  file.bw[[i]]=channel(filename[[i]],mode="grey")
  display(file.bw[[i]])
}

for (i in 1:5) {
  file.bl[[i]]=channel(filename[[i]], mode='asblue')
  display(channel(filename[[i]], mode='asblue'))
}

for (i in 1:5) {
  file.red[[i]]=channel(filename[[i]], mode='asred')
  display(channel(filename[[i]], mode='asred'))
}
```


#Extract the texture by high contrast on blue channel, 
which really shows difference to me between fried chicken and dogs.
```{r}
file.contrast=list()
for (i in 1:5){
  file.contrast=file.bl[[i]]*5
  display(file.bl[[i]]*5)
}
```

#Filtering: high pass
```{r}
filter_high <- matrix(1, nc = 3, nr = 3)
filter_high[2, 2] <- -8
file.hi=list()
for (i in 1:5){
  file.hi <- filter2(filename[[i]], filter_high)
  display(file.hi)# high pass
}
```

#Adaptive thresholding
```{r}
for (i in 1:5){
  file.bw[[i]]=channel(filename[[i]],mode="grey")
  img_seg1 <- thresh(file.bw[[i]], w=60, h=60, offset=0.06)
  display(img_seg1, all=TRUE)
}
```


# Outline Analysis
```{r}
#Oriented Contour ### didn't see any use here
img_leaf=list()
img_leaf1=list()
oc=list()

for (i in 1:5){
  img_leaf[[i]] <- resize(filename[[i]], 128, 128)
  img_leaf[[i]] <- channel(img_leaf[[i]], mode="gray")
  img_leaf1[[i]] <- thresh(img_leaf[[i]], w=50, h=50, offset=0.05)
  display(img_leaf1[[i]])}

for (i in 1:5){
  oc[[i]] <- ocontour(bwlabel(img_leaf1[[i]]))
  plot(oc[[i]][[1]], type='l');points(oc[[i]][[1]], col=2)
}
```

```{r}
#Local Curvature
lc=list()
i=list()
neg=list()
pos=list()

for (k in 1:5){
  lc[[k]] <- localCurvature(x=oc[[k]][[1]], h=11)
  i[[k]] <- lc[[k]]$curvature >= 0
  neg[[k]] <- array(0, dim(img_leaf1[[k]]))
  pos[[k]] <- neg[[k]]
  pos[[k]][lc[[k]]$contour[i[[k]],]+1]  <- lc[[k]]$curvature[i[[k]]]
  neg[[k]][lc[[k]]$contour[!i[[k]],]+1] <- -lc[[k]]$curvature[!i[[k]]]
  display(10*(rgbImage(pos[[k]], , neg[[k]])), title = "Image curvature")
}
```

#Color Features from RGB

By discretizing the RGB values, we can get a set of color features. We subdivide the pixel values in each color channel into multiple bands of equal width. Then the counts of pixels in correponding bins consist of a set of color features that characterizes the color distribution of the image.
```{r}
mat=list()
freq_rgb=list()
rgb_feature=list()

nR <- 10
nG <- 8
nB <- 10 # Caution: the bins should be consistent across all images!
rBin <- seq(0, 1, length.out=nR)
gBin <- seq(0, 1, length.out=nG)
bBin <- seq(0, 1, length.out=nB)

for (i in 1:5){
  mat[[i]] <- imageData(filename[[i]])
  freq_rgb[[i]] <- as.data.frame(table(factor(findInterval(mat[[i]][,,1], rBin), levels=1:nR), factor(findInterval(mat[[i]][,,2], gBin), levels=1:nG), factor(findInterval(mat[[i]][,,3], bBin), levels=1:nB)))
  rgb_feature[[i]] <- as.numeric(freq_rgb[[i]]$Freq)/(ncol(mat[[i]])*nrow(mat[[i]])) # normalization
}

str(rgb_feature) #each image has 800 features
#The number of bins for each color channel (nR,nG,nB) is a tuning parameter for constructing color features. The total number of features is nR*nG*nB.
```

#Color Features From HSV

The Hue, Saturation, Value (HSV) model of color is closer to human perception of color, and thus is eaiser to interpret than RGB model. Using the same discretization, color features can be extracted from the histogram of HSV values.
```{r}
library(grDevices)

nH <- 10
nS <- 6
nV <- 6
# Caution: determine the bins using all images! The bins should be consistent across all images. The following code is only used for demonstration on a single image.
hBin <- seq(0, 1, length.out=nH)
sBin <- seq(0, 1, length.out=nS)
vBin <- seq(0, 0.005, length.out=nV) 

# Convert 3d array of RGB to 2d matrix

mat_rgb <- mat
mat_hsv <- list()
freq_hsv <- list()
hsv_feature <- list()

for (i in 1:5){
  dim(mat_rgb[[i]]) <- c(nrow(mat[[i]])*ncol(mat[[i]]), 3)
  mat_hsv[[i]] <- rgb2hsv(t(mat_rgb[[i]]))

  freq_hsv[[i]] <- as.data.frame(table(factor(findInterval(mat_hsv[[i]][1,], hBin), levels=1:nH), factor(findInterval(mat_hsv[[i]][2,], sBin), levels=1:nS),  factor(findInterval(mat_hsv[[i]][3,], vBin), levels=1:nV)))
  
  hsv_feature[[i]] <- as.numeric(freq_hsv[[i]]$Freq)/(ncol(mat[[i]])*nrow(mat[[i]])) # normalization
}
str(hsv_feature) # 360 HSV features
#The number of bins for each model (nH,nS,nV) is a tuning parameter for constructing color features. The total number of features is nHnSnV.
```

