---
title: "Random Forest"
output: html_notebook
---
I am using data preprocessing code directly from decision_tree.R
```{r}
# code from decision_tree.R

library(data.table)
sift= fread("sift_features.csv", header= F)
labels <- dir("images")
filelabel= as.numeric(substr(labels, 1,1) == "c")
labels= substr(labels,1,nchar(labels)-4)
labels.df = data.frame(filename= labels, filelabel= filelabel)

sift.df= as.data.frame(t(sift))
colnames(sift.df)[1] <- "filename"

data.all= merge(sift.df,labels.df, by= names(sift.df)[1])[,-1]
data.all = as.data.frame(apply(data.all,2, as.numeric))
data.all$filelabel = as.factor(data.all$filelabel)
#############################################################

# Split data into testing and training using 
set.seed(2)
train=sample(1:nrow(data.all),nrow(data.all)*0.8)
test=-train
train_data=data.all[train,]
test_data=data.all[test,]
test_label=filelabel[test]
```

Just use variables in dicision_tree.R
train_data
test_data

```{r}
library(randomForest)
### Make formula
varNames <- names(train_data)
# Exclude ID or Response variable
varNames <- varNames[!varNames %in% c("filelabel")]
# add + sign between exploratory variables
varNames1 <- paste(varNames, collapse = "+")
# Add response variable and convert to a formula object
rf.form <- as.formula(paste("filelabel", varNames1, sep = " ~ "))
```


Random Forest business starts.
```{r}
library(randomForest)
rf=randomForest(rf.form,train_data,ntree=500,importance=T) # It really took tens of minutes
plot(rf)
```
500 decision trees or a forest has been built using the Random Forest algorithm based learning. We can plot the error rate across decision trees. Black solid line is OOB error rate and colour lines for each class' error. The plot seems to indicate that after 300 decision trees, there is not a significant reduction in error rate.

*OOB is the mean prediction error on each training sample xi, using only the trees that did not have xi in their bootstrap sample. 


Prediction perforamace for training data
```{r}
# Predicting response variable
train_data$predicted.response <- predict(rf ,train_data)

# Load Library or packages
library(e1071)
library(caret)
# Create Confusion Matrix
confusionMatrix(data=train_data$predicted.response,reference=train_data$filelabel,positive='1')
```

Predict for testing data
```{r}
# Predicting response variable
test_data$predicted.response <- predict(rf,test_data)

# Create Confusion Matrix
confusionMatrix(data=test_data$predicted.response,
                reference=test_data$filelabel,
                positive='1') # prediction accuracy rate is 62.75%

```




